---
title: "RobustRegression"
author: "Dan Ovando"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RobustRegression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package prodives a function `RobustRegression` that allows users to run linear regression with heteroskedastic robust standard errors, as well as clustered standard errors. The function returns a list object with a variety of useful outputs.

Let's start by running a simple linear regression using the `iris` dataset included with R.

```{r load things, message=F, warning=F}
library(RobustRegression)
library(stargazer)

data("iris")

iris <- as_data_frame(iris)

head(iris)

```

Iris contains information on flower traits for a number of different species of iris. Suppose we want to run a regression. We want to run a regression predicting the sepal length (`Sepal.Length`) as a function of sepal width (`Sepal.Width`), petal length (`Petal.Length`), and the species of iris (`Species`). Note that `Species` variable is categorical. 

We are worried both that errors might be heterskedastic and clustered. Perhaps for example the variability in sepal length in creases with petal length (heteroskedasticity), or that each species of iris have similar and different types of error structures (clustering). Ordinarily, we might run a simple linear regression of the form ` lm(Sepal.Length ~ Sepal.Width + Petal.Length + Species, data = iris)`. However, we want to account for this heteroskedasticity and clustering. 

In STATA, we could accomplish this through 

`regress Sepal.Length Sepal.Width Petal.Length i.Species, robust cluster(Species)`

In R, we will instead use the `RobustRegression` function:

```{r run regression}
regression <-  RobustRegression(model = lm(Sepal.Length ~ Sepal.Width + Petal.Length + Species, data = iris),
                 dat = iris, cluster_var = 'Species')
```

We simply specify a `model` in the same manner as we normally would. `RobustRegression` automatically calcualtes robust standard errors and p values. The default value for `cluster_var` is 'None'. In this case, we want to cluster errors by `"Species"`. 


`regression` is a list that contains a number of useful data frames and objects. 

  * `regression$`
    * `model` is the standard model object produced by `lm`, except that an object called `model$RobustSEs` has been added that include the robust standard errors. Note that functions such as `summary` calculate things like p values and standard errors on the fly from the data, and so will not show robust standard errors if used
    * `TidyModel` is a tidyed data frame with the model, containing the coefficients, standard standard errors, and various test statistics
    * `AugModel` is the original data frame used in the regression, with augmented variables such as fitted values
    * `GlanceModel` contains a tidyed data frame of model summary statistics, e.g. R^2^
    * `RegPlot` a plot of the regression coefficients
    
We can use the `stargazer` package to make nice table summaries of our results, with and without heteroskedastic robust and clustered standard errors. 

```{r display regression, results = 'asis'}


stargazer(regression$model, type = 'html', se = list(regression$TidyModel$RobustSE), p = list(regression$TidyModel$RobustPvalue), t.auto = T, p.auto = T, title = 'Robust and Clustered Standard Errors')

stargazer(regression$model, type = 'html', 
          title = 'Basic Standard Errors')

```

As we would expect, using `RobustRegression` doesn't change our estimated model coefficients at all, but accounting for clusters and heteroskedasticity does substantially change the standard errors and p values
